An in-depth study of Explainability and Adversarial Robustness for RNNs

### 2019-12-16 ex3/paper/paper.tex
Other small modification to ARS section
Normal->benign and minor text changes

$\delta \in \mathbb R$ determines the logit output of successful adversarial.
In the original publication $\delta=0$, which means that the network's decision for adversarial samples is just between attack and normal traffic. In the present context, we need to make sure that the classifier's prediction would actually be normal traffic, even though a certain level of noise will be added to \glspl{iat} due to the network between attacker and victim. Hence, we introduced $\delta=-0.2$, corresponding to a confidence of 55\% for the sample to be benign.

@@

As expected, \gls{cw}  delivers the best performance and FGSM, while being the fastest of all investigated algorithms, delivers the worst performance.
%\autoref{fig:adv_per_family} depicts how successful the attack is for individual attack families.
The figure shows significant differences for detecting different attack families in the first place. However, also for generating adversarial flows some attack families are more susceptible than others. However, the results match to a high degree with our expectations. For example, SQL injection attacks apparently are closer to normal traffic than \gls{dos} attacks and, hence, finding adversarial samples should be easier.

@@

The result is a number of adversarial samples and some that could not be made adversarial. If at least half of the samples are misclassified, we take 50\% of the samples, with those that required smaller modifications first. Of these samples, the distance of each adversarial sample to the original sample is taken and averaged. The resulting average distance is the \gls{ars}. The larger it is the better since then an adversary needs to modify the samples more to make them adversarial. If not more then half of the samples could be made adversarial, our metric is undefined since then apparently it is not possible for an adversary to reliably conduct adversarial attacks on the majority of samples. Setting the threshold for the \gls{ars} to 50\% is arbitrary, but
 % reasonable as this way the \gls{ars} approximates the median of the distances of all samples and, additionally, marks the distance where an adversarial attack is more likely to be successful than unsuccessful.
 reasonable as outliers with very large distances are ignored and if an attacker can make the majority of samples adversarial, we think that its attack is ``successful''.
%we think that it is reasonable since if an attacker can make the majority of samples adversarial, we think that its attack is ``successful''.

@@

\subsection{Adversarial training}
As alternative to omitting manipulable features, we attempted to make the classifier more robust against adversarial samples by augmenting the training set by adversarial flows generated using  \gls{cw}, labeled as additional attacks.

For this purpose, we added one adversarial sample per attack sample to the training set. Since \gls{cw} is deterministic, this is the maximum number of adversarial samples possible. With this training set we then alternated retraining of the neural network and optimization of the adversarial samples using gradient descent.

@@

\autoref{fig:avdistance} shows the \gls{ars} throughout the adversarial training procedure for several attack categories and clearly indicates that adversarial training is effective, as the distance gradually increases. Hence, an attacker would have to modify attack samples more and more, eventually rendering the attack unpractical.

@@

For both datasets, after a small number of epochs, it was no longer possible to create a significant number of adversarial samples for most attack categories. %For the datasets we considered, adversarial training left classification performance unaffected.
%\todo{Max: Insert results that show that accuracy on normal data is still ok after adversarial training.}
%\autoref{tab:adv_training_performance} depicts classification on non-adversarial data after 50 epochs of adversarial training.
After 50 epochs of training, accuracy is essentially identical to results presented in \autoref{tab:performance_results}. Recall and Youden increased and precision slightly decreased. However, this is due to the higher proportion of attack samples in training data.
We conclude that adversarial training is effective for reducing the attack surface for adversarial attacks in our scenario.

>>>>

$\delta \in \mathbb R$ determines the logit output of successful adversarial.
In the original publication $\delta=0$, which means that the network's decision for adversarial samples is just between attack and benign traffic. In the present context, we need to make sure that the classifier's prediction would actually be benign, even though a certain level of noise will be added to \glspl{iat} due to the network between attacker and victim. Hence, we introduced $\delta=-0.2$, corresponding to a confidence of 55\% for the sample to be benign.

@@

As expected, \gls{cw}  delivers the best performance and FGSM, while being the fastest of all investigated algorithms, delivers the worst performance.
%\autoref{fig:adv_per_family} depicts how successful the attack is for individual attack families.
The figure shows significant differences for detecting different attack families in the first place. However, also for generating adversarial flows some attack families are more susceptible than others. However, the results match to a high degree with our expectations. For example, SQL injection attacks apparently are closer to benign traffic than \gls{dos} attacks and, hence, finding adversarial samples should be easier.

@@

The result is a number of adversarial samples and some that could not be made adversarial. If at least half of the samples are misclassified, we take 50\% of the samples, with those that required smaller modifications first. Of these samples, the distance of each adversarial sample to the original sample is taken and averaged. The resulting average distance is the \gls{ars}. The larger it is the better since then an adversary needs to modify the samples more to make them adversarial. If not more then half of the samples could be made adversarial, our metric is undefined since then apparently it is not possible for an adversary to reliably conduct adversarial attacks on the majority of samples. Then the ratio of samples that could be made adversarial (<50\%) can be useful metric to determine the exact extent of the adversarial threat. Setting the threshold for the \gls{ars} to 50\% is arbitrary, but
 % reasonable as this way the \gls{ars} approximates the median of the distances of all samples and, additionally, marks the distance where an adversarial attack is more likely to be successful than unsuccessful.
 reasonable as outliers with very large distances are ignored and if an attacker can make the majority of samples adversarial, we think that its attack is ``successful''. 
%we think that it is reasonable since if an attacker can make the majority of samples adversarial, we think that its attack is ``successful''.

@@

\subsection{Adversarial training}
As alternative to omitting manipulable features, we attempted to make the classifier more robust against adversarial samples by augmenting the training set by adversarial flows generated using  \gls{cw}, labeled as additional attacks.
For this purpose, we added one adversarial sample per attack sample to the training set. Since \gls{cw} is deterministic, this is the maximum number of adversarial samples possible. With this augmented training set we then alternated retraining of the neural network and optimization of the adversarial samples. % using gradient descent.

@@

\autoref{fig:avdistance} shows the \gls{ars} throughout  adversarial training  for several attack categories and clearly indicates that adversarial training is effective, as the distance gradually increases. Hence, an attacker would have to modify attack samples more and more, eventually rendering the attack unpractical.

@@

For both datasets, after a small number of epochs, it was no longer possible to create a significant number of adversarial samples for most attack categories. %For the datasets we considered, adversarial training left classification performance unaffected.
%\todo{Max: Insert results that show that accuracy on normal data is still ok after adversarial training.}
%\autoref{tab:adv_training_performance} depicts classification on non-adversarial data after 50 epochs of adversarial training.
After 50 epochs of training, accuracy is essentially identical to the results presented in \autoref{tab:performance_results}. Recall and Youden increased and precision slightly decreased. However, this is due to the higher proportion of attack samples in training data and, hence, expected.
We conclude that adversarial training is effective for reducing the attack surface for adversarial attacks in our scenario.
